---
title: "Power Analysis for Logistic Regression Models"
author: "jlgonrod"
date: "2024-08-22"
output: html_document
---

# Introduction
In this document, we will perform a power analysis for three logistic regression models. We will also adjust the sample size to account for an expected dropout rate of 10%.

# Load Libraries and Data
First, we load the necessary libraries and the dataset in Feather format.

```{r}
# Install and load the required libraries
#install.packages("pwr")
#install.packages("arrow")
library(pwr)
#library(arrow)

# Load the dataset in Feather format
data <- read.csv("data/df_clean_EII.csv")

# Display the first few rows of the dataset for verification
head(data)
```

# Initial Parameters
Next, we define the parameters for the power analysis:

```{r}
# Define parameters
f2 <- 0.15  # Medium effect size
u <- ncol(data) - 1  # Number of predictors
power_level <- 0.8  # Desired power level
dropout_rate <- 0.10  # Dropout rate of 10%
```

#Power Analysis and Sample Size Adjustment
We perform the power analysis for each model and adjust the sample size to account for the dropout rate.

```{r}
# Model 1: res_clin_26
sample_size_model <- pwr.f2.test(u = u, f2 = f2, sig.level = 0.05, power = power_level)$v
adjusted_sample_size_model <- sample_size_model / (1 - dropout_rate)

n_model_1 <- 227
n_model_2 <- 227
n_model_3 <- 227

n_model_crohn_vedo_res52 <- 45
n_model_crohn_vedo_rem52 <- 45

n_model_ulce_vedo_res52 <- 47
n_model_ulce_vedo_rem52 <- 47

n_model_crohn_uste_res52 <- 124
n_model_crohn_uste_rem52 <- 124

n_model_ulce_uste_res52 <- 11
n_model_ulce_uste_rem52 <- 11

# Print the results
cat("Model with", u, "features:\n")
cat("Initial sample size required:", ceiling(sample_size_model), "\n")
cat("Adjusted sample size required (10% dropout):", ceiling(adjusted_sample_size_model), "\n\n")

cat("N model res_clin_26(training 75%):", ceiling(n_model_1*0.75), "\n")
cat("N model res_clin_52(training 75%):", ceiling(n_model_2*0.75), "\n")
cat("N model rem_clin_52(training 75%):", ceiling(n_model_3*0.75), "\n")

cat("N model Crohn's disease + VEDO res_clin_52(training 75%):", ceiling(n_model_crohn_vedo_res52*0.75), "\n")
cat("N model Crohn's disease + VEDO rem_clin_52(training 75%):", ceiling(n_model_crohn_vedo_rem52*0.75), "\n")

cat("N model Ulceralive Colitis + VEDO res_clin_52(training 75%):", ceiling(n_model_ulce_vedo_res52*0.75), "\n")
cat("N model Ulceralive Colitis + VEDO rem_clin_52(training 75%):", ceiling(n_model_ulce_vedo_rem52*0.75), "\n")

cat("N model Crohn's disease + USTE res_clin_52(training 75%):", ceiling(n_model_crohn_uste_res52*0.75), "\n")
cat("N model Crohn's disease + USTE rem_clin_52(training 75%):", ceiling(n_model_crohn_uste_rem52*0.75), "\n")

cat("N model Ulceralive Colitis + USTE res_clin_52(training 75%):", ceiling(n_model_ulce_uste_res52*0.75), "\n")
cat("N model Ulceralive Colitis + USTE rem_clin_52(training 75%):", ceiling(n_model_ulce_uste_rem52*0.75), "\n")
```

``
